Data Exploration

### 2019-02-21 src/data_exploration.Rmd
make loop clever

asclist <- (list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*_86.9294*.asc"), full.names = TRUE))    # this folder currently contains other dummy files. its just a test to automate stacks
ascfile <- names(asclist[[1]])
ascyear <- as.character(sapply(strsplit(ascfile[[1]], "_"), "[[", 1))
ascmonth <- as.character(sapply(strsplit(ascfile[[1]], "_"), "[[", 2))
ascdepth <- as.character(sapply(strsplit(ascfile[[1]], "_"), "[[", 5))
ascname <- paste(ascyear, ascmonth, ascdepth, sep = "_") #once you figure out how to rename the layers in the stack, you will rename the stack this () or not - maybe just manual
asclist # now need to rename to match maxent expectations

>>>>

```{r}
```{r}
system.file("java", package="dismo") #finding location to put maxent jar file
system("java -version")
```

messing with code to see if can do for unique year month depth
```{r}
ascname <- list.files("../data/jan_test_86.9", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks
noasc <- length(ascname)
  year <- "1998"
  month <- "01"
  depth <- "86.9294.asc"
  tempvar <- "temp"
  chlvar <- "chl"
  o2var <- "o2"
  salvar <- "salinity"
  depthvar <- "depth"
  surfacevar <- "surface"
  naovar <- "nao"
  amovar <- "amo"
  samplevar <- "sample"
  wintervar <- "winter"

}
```
